---
title: "Maternal Health Risk in Rural Areas of Bangladesh"
author: "Victoria Chang"
date: "`r Sys.Date()`"
output: html_document
---

## Introduction

### Dataset description

Data from a select group of pregnant women at various healthcare centers in
rural areas of Bangladesh were collected. The dataset includes continuous
variables age, systolic blood pressure, diastolic blood pressure, blood sugar,
body temperature, and heart rate which were collected via wearable health
sensors. One categorical variable, predicted risk level for maternal mortality,
is also included.  

### Analysis objectives

The first aim of this report is to determine whether there are significant
differences in blood pressure and blood pressure between low and high maternal
mortality risk levels using t-tests.  

The second aim of this report is to run a simple linear regression and depict a
scatterplot between age and blood sugar, which will help elucidate any potential
association between the two variables. 

Together, these statistical analyses can help inform scientific inquiry into
potential relationships between variables such as blood pressure, blood sugar,
age, and level of maternal mortality risk in rural Bangladesh communities.
Results may help inform targets for intervention to reduce maternal mortality
risk in rural areas of Bangladesh.

```{r, set-chunk-opts, echo = FALSE}
library(knitr) # load packages

# set global chunk options
opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE
) 

```


```{r read-dataset}

# Set filepaths
here::i_am("Final_Analysis.Rmd") # declare location of current report

wd <- here::here() # Set path for project root directory
dir.create(file.path(wd, "raw_data"), showWarnings = FALSE) # create raw_data folder

setwd(file.path(wd)) # set working directory

# Load data
data <- read.csv(
  file = here::here("raw_data/raw_data.csv") 
)


```







The below table shows the descriptive statistics of all variables such as age,
blood sugar, blood pressure, temperature, and heart rate in the dataset
stratified by maternal mortality risk level (Median and IQR for Age; Mean and
Standard Deviation for all other variables).


```{r descriptive-table}

# Load table1 from output/ folder
table_one <- readRDS(
  file = here::here("output", "table_one.rds")
)

table_one # Output table


```


The below table depicts the p-value statistics from the t-tests comparing
blood pressure and blood sugar variables between pregnant women with low and
high risk maternal mortality.


```{r t-test-table}

# Load table_two from output/ folder
table_two <- readRDS(
  file = here::here("output", "table_two.rds")
)

table_two # Output table

```



```{r regression}

# Load regression from output/ folder
reg1 <- readRDS(
  file = here::here("output", "reg1.rds")
)

```

The adjusted R-squared of the linear regression model between age and blood
sugar is `r summary(reg1)$adj.r.squared`. The figure below shows a scatterplot
of age (years) and blood sugar (mmol/L) with a linear regression model of the
two variables overlayed. 


```{r descriptive-figure}
#| fig.align = "center",
#| out.width = "600px"

# Load graph
knitr::include_graphics(
  here::here("output/scatterplot.png")
)
```

